Cover letter for the original IJRR submission

### 2017-12-12 body/appendix_algo.tex
typos

From the start configuration, given as an input by the user,
we create the initial state $s0$. A state is described by a whole-body configuration, as well as the list of currently active contacts.
Algorithm~\ref{alg:interpolate}  is then called with $s0$, as well as the discretized path 
$\mathbf{Q}^0$, as input parameters.

\begin{algorithm}[!tbp]
\caption{Discretization of a path} \label{interpolate}
	\begin{algorithmic}[1]
	%~ \Function{GenerateConfiguration}{}
	\Function{Interpolate}{$s0$,$\mathbf{Q}^0$, $MAX\_TRIES$}
		\State $states \gets (s0)$ \Comment{List of states intialized with $s0$}
		\State $nb\_fail \gets 0$ 
		\State $i \gets 1;$ \Comment{Current index in the list}
		\While {$i < length(\mathbf{Q}^0)$}
			\State $pState \gets last\_element(states)$
			\State $s \gets$ \textsc{GenFullBody}$(pState, element(\mathbf{Q}^0,i))$
			\If {$s \not= 0 $}
				\State $nb\_fail \gets 0$
				\State $i \gets i+1$
				%~ \State \textbf{return} $\mathbf{q}^{0}$
			\Else
				\State $nb\_fail \gets nb\_fail + 1$
				%~ \If {$nb\_fail == MAX\_TRIES$}
					%~ \State \textbf{return} $FAILURE$
				%~ \EndIf				
				\State $s \gets $\textsc{IntermediateContactState}$(pState)$
				\If {$s == 0 \lor nb\_fail == MAX\_TRIES$}
					\State \textbf{return} $FAILURE$
				\EndIf		
			\EndIf
			\State $push\_back(states, s)$
		\EndWhile
		\State \textbf{return} $states$
	\EndFunction
\end{algorithmic}
\label{alg:interpolate}
\end{algorithm}

@@

The method \textsc{IsInStaticEquilibrium} returns whether a given state is in static equilibrium. $CreateState$ creates a new state, given
a configuration and the list of active contacts.
$ContactLimbs$ (respectively $FreeLimbs$) returns the list of limbs that are in contact (respectively \textit{not} in contact).  $MarkContact$ (respectively $MarkFree$)  marks a limb as in contact (respectively \textit{not} in contact). These methods follow a FIFO approach: the first Limb chronologically marked as in contact (respectively not in contact) is returned first by $ContactLimbs$ (respectively $FreeLimbs$). This allows the algorithm to be deterministic even though it can handle acyclic motions.
%~ $add\_contact\_limb(newState,k)$ marks a limb as in contact at a given state.

>>>>

From the start configuration, given as an input by the user,
we create the initial state $s0$. A state is described by a whole-body configuration, as well as the list of currently active contacts and their associated 6D positions.
Algorithm~\ref{alg:interpolate}  is then called with $s0$, as well as the discretized path 
$\mathbf{Q}^0$, as input parameters.

\begin{algorithm}[!tbp]
\caption{Discretization of a path} \label{interpolate}
	\begin{algorithmic}[1]
	%~ \Function{GenerateConfiguration}{}
	\Function{Interpolate}{$s0$,$\mathbf{Q}^0$, $MAX\_TRIES$}
		\State $states \gets (s0)$ \Comment{List of states initialized with $s0$}
		\State $nb\_fail \gets 0$ 
		\State $i \gets 1;$ \Comment{Current index in the list}
		\While {$i < length(\mathbf{Q}^0)$}
			\State $pState \gets last\_element(states)$
			\State $s \gets$ \textsc{GenFullBody}$(pState, element(\mathbf{Q}^0,i))$
			\If {$s \not= 0 $}
				\State $nb\_fail \gets 0$
				\State $i \gets i+1$
				%~ \State \textbf{return} $\mathbf{q}^{0}$
			\Else
				\State $nb\_fail \gets nb\_fail + 1$
				%~ \If {$nb\_fail == MAX\_TRIES$}
					%~ \State \textbf{return} $FAILURE$
				%~ \EndIf				
				\State $s \gets $\textsc{IntermediateContactState}$(pState)$
				\If {$s == 0 \lor nb\_fail == MAX\_TRIES$}
					\State \textbf{return} $FAILURE$
				\EndIf		
			\EndIf
			\State $push\_back(states, s)$
		\EndWhile
		\State \textbf{return} $states$
	\EndFunction
\end{algorithmic}
\label{alg:interpolate}
\end{algorithm}

@@

The method \textsc{IsInStaticEquilibrium} returns whether a given state is in static equilibrium. $CreateState$ creates a new state, given
a root configuration and the list of active contacts.
$ContactLimbs$ (respectively $FreeLimbs$) returns the list of limbs that are in contact (respectively \textit{not} in contact).  $MarkContact$ (respectively $MarkFree$)  marks a limb as in contact (respectively \textit{not} in contact). These methods follow a FIFO approach: the first Limb chronologically marked as in contact (respectively not in contact) is returned first by $ContactLimbs$ (respectively $FreeLimbs$). This allows the algorithm to be deterministic even though it can handle acyclic motions.
%~ $add\_contact\_limb(newState,k)$ marks a limb as in contact at a given state.
